### 2024-06-05 draft.qmd
20240604 - links
20240605 - VORP

@@

An important concept in the snake draft is a player's value over a typical replacement player at that position (shortened to "value over replacement player"), which is described in Section @sec-fantasyValue.
A player's *value over a replacement player* (VORP) is the difference between (a) a player's projected fantasy points and (b) the fantasy points that you would be expected to get from a typical bench player at that position.

>>>>

Section @sec-fantasyValue describes where to obtain aggregated rankings, aggregated projections, ADP, and AAV data.

@@

An important concept in the snake draft is a player's value over a typical replacement player at that position (shortened to "value over replacement player"; VORP), which is described in Section @sec-fantasyValue.
In general, your goal is to draft the team whose weekly starting lineup has the greatest VORP.

### 2024-06-05 player-evaluation.qmd
20240605 - VORP

A player's *dropoff*, is the difference between (a) the player's projected points and (b) the projected points of the next-best player at that position.
We can also consider a player's value over a typical replacement player at that position (shortened to "value over replacement player").
A player's *value over a replacement player* (VORP) is the difference between (a) a player's projected fantasy points and (b) the fantasy points that you would be expected to get from a typical bench player at that position.

>>>>

A player's *dropoff* is the difference between (a) the player's projected points and (b) the projected points of the next-best player at that position.

Because players from some positions (e.g., Quarterbacks) tend to score more points than players from other positions (e.g., Wide Receivers), it would be inadvisable to compare players across different positions based on projected points.
In order to more fairly compare players across positions, we can consider a player's value over a typical replacement player at that position (shortened to "value over replacement player").
A player's *value over a replacement player* (VORP) is the difference between (a) a player's projected fantasy points and (b) the fantasy points that you would be expected to get from a typical bench player at that position.
Thus, VORP provides an index of how much added value a player provides.
